### 2022-03-15 manuscript.tex
png [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/1641e91da2ea2e649fd5023d29243d56df558151.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/1641e91da2ea2e649fd5023d29243d56df558151/checks
https://github.com/scherzerthesis/thesis/actions/runs/1987465324

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/4b1908f3c716a7c3969493bbc367cb5b13788648/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/4b1908f3c716a7c3969493bbc367cb5b13788648}{scherzerthesis/thesis@4b1908f}
on March 15, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:05}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba2.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:05}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba3.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:07}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba4.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:07}
}
\end{figure}

\begin{figure}
\hypertarget{fig:08}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba5.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:08}
}
\end{figure}

\begin{figure}
\hypertarget{fig:09}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba6.tif}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:09}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/1641e91da2ea2e649fd5023d29243d56df558151/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/1641e91da2ea2e649fd5023d29243d56df558151}{scherzerthesis/thesis@1641e91}
on March 15, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:05}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba2.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:05}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba3.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:07}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba4.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:07}
}
\end{figure}

\begin{figure}
\hypertarget{fig:08}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba5.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:08}
}
\end{figure}

\begin{figure}
\hypertarget{fig:09}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba6.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:09}
}
\end{figure}
